---
title: "Replication Code"
subtitle: "Racialization and Perceived Institutional Ideology"
author:
  - name: Karla Magaña
    affiliations:
      - name: University of Michigan
    #department: Department of Political Science
    email: "kmagana@umich.edu"
    attributes:
      corresponding: true
  - name: Devin Judge-Lord
    affiliations:
      - name: University of Michigan
    #department: Ford School of Public Policy
format:
    html: 
      toc: true
      code-fold: true
editor_options: 
  chunk_output_type: console
---


```{r global.options, include=FALSE}
testing = F

library(modelsummary)
library(marginaleffects)
# library(fixest)
library(tidyverse)
library(magrittr)
library(knitr)
library(kableExtra)
library(here)
library(ggrepel)

knitr::opts_chunk$set(echo = T, # code is folded 
                      cache = F, # CACHE 
                      fig.width = 4.5, 
                      fig.height = 3.5,
                      split = T,
                      fig.align = 'center', 
                      fig.path='figs/',
                      fig.retina = 6,
                      warning = F, 
                      message = F)

# inline numbers round to 2, comma at thousands
inline <- function(x) {
  if (is.na(as.numeric(x))) {
    return (x)
    } else
        return (as.numeric(x) |> 
                 round(2) |>
                 format(big.mark=",") 
        )
}

knitr::knit_hooks$set(inline = inline)

# plot defaults 
library(ggplot2); theme_set(
      theme_minimal() + 
        theme(
          # FOR AJPS
          #panel.grid = element_blank(),
          #legend.position = "bottom",
          # END FOR AJPS 
          panel.border  = element_blank(),
          panel.grid.major.x = element_blank())
                            )
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
  scale_color_discrete <- function(...)
    scale_color_viridis_d(..., option = "inferno", begin = .2, end = .8, direction = 1)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(..., option = "inferno", begin = .2, end = .8, direction = 1)
  
# html table formatting
kablebox <- . %>%  
  head(100) %>%
  knitr::kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "200px")

kablebox_long <- . %>% 
  head(100) %>% 
  knitr::kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "500px")
```



#TODO 

- [ ] 


```{r cm, include=FALSE}
# directory to store model objects 
if (!dir.exists(here::here("models"))) {dir.create(here::here("models"))}


# Coef Map
cm = c("Perceived Ideology" = "Perceived ideology",
       "log(total_staff)" = "Log(Total Staff)",
        "log(annual_budget_usd)" = "Log(Budget)", 
       "Agency" = "Agency",
       "department_agency_acronym", "Agency",
       "Num.Obs." = "Observations"
       )


# set fixed effects mapping 
# setFixest_dict(cm)

format_n <- function(x) format(round(x, 3), big.mark=",") # this works
f <- function(x) stringr::str_replace(x, "[A-z]", "✓") #FIXME not sure why this is not working

gm <- list(
  list("raw" = "nobs", "clean" = "Observations", "fmt" = format_n)
)
```

# Data

## Agency name crosswalk 

```{r crosswalk}
# From code/get_crosswalk.R
load(here::here("data", "crosswalk.rda"))

crosswalk |> kablebox()
```

## Project 2025 

<https://github.com/judgelord/2025>

"mfl_data"

```{r }
#| fig-width: 5.1
#| fig-height: 5
#| layout-ncol: 1
#| label: mfl_data

# from https://github.com/judgelord/2025
# modified with code/get_data_2025.R
load(here::here("data", "mfl.rda"))

mfl |> kablebox()

mfl %<>% left_join(crosswalk)

n_mfl_racial<- sum(mfl$MFL_n)
n_mfl_total <- sum(mfl$MFL_total)
n_mfl_agencies <- distinct(mfl, department_agency_acronym) |> nrow()

# mfl |> count(department_agency_acronym, sort = T)

mfl |> 
  filter(agency == department_agency_acronym) |> 
  drop_na(department) |> 
  ggplot() + 
  aes(x = MFL_n, 
      y = reorder(department, MFL_n) 
      ) + 
  geom_col() + 
  labs(x = "Racialized Words per Section", 
       y = "")

mfl |> 
  filter(agency == department_agency_acronym) |> 
  drop_na(department) |> 
  ggplot() + 
  aes(x = MFL_percent, 
      y = reorder(department, MFL_percent) 
      ) + 
  geom_col() + 
  labs(x = "Racialized Words per Paragraph", 
       y = "")
```

## NYT 

From ProQuest

"nyt_data"

```{r}
#| fig-width: 5.3
#| fig-height: 4
#| layout-ncol: 1
#| label: nyt_data

# from code/get_data_nyt.R
# + docs/trends-nyt.qmd
load(here::here("data", "nyt.rda") ) 

nyt  |> kablebox()

n_nyt_articles <- sum(nyt$total)
n_nyt_racial <- sum(nyt$term_count)
n_nyt_agencies <- length(unique(nyt$department_agency_acronym))

#FIXME BRING BACK A BY-YEAR VERSION AT SOME POINT 
nyt %<>% 
  group_by(department_agency_acronym, agency) %>% 
  summarise(total = sum(total, na.rm = T),
            term_count = sum(term_count, na.rm = T)) %>%
  ungroup() %>% 
  mutate(
    total = sqrt(total), 
    NYT_n = term_count,
                n = sqrt(term_count),
                NYT_norm = (n - mean(n))/sd(n),
                  percent = n/total,
                  NYT_percent_norm =  (percent - mean(percent))/sd(percent)) %>%
  select(agency, NYT_n, percent, NYT_norm, NYT_percent_norm, department_agency_acronym) %>% 
  ungroup()


nyt %<>% left_join(crosswalk)

nyt |> 
  filter(agency == department_agency_acronym) |> 
  drop_na(department) |> 
  ggplot() + 
  aes(x = NYT_n, 
      y = reorder(department, NYT_n) ) + 
  geom_col() + 
  labs(x = "Articles with Racial Words", 
       y = "")

nyt |> 
  filter(agency == department_agency_acronym) |> 
  drop_na(department) |> 
  ggplot() + 
  aes(x = percent, 
      y = reorder(department, percent) ) + 
  geom_col() + 
  labs(x = "Share of Articles with Racial Words", 
       y = "")

nyt %<>% select(-percent)
```

## Rules 

<https://github.com/judgelord/regulationsdotgov>

"rules_data"

```{r}
#| fig-width: 6
#| fig-height: 8.5
#| layout-ncol: 1
#| label: rules_data

# from https://github.com/judgelord/regulationsdotgov
# modified with code/get_data_rules.R
# FIXME - include the total so that we can make the summary stats here and load just one dataframe, rules.rda
load(here::here("data", "rules.Rdata"))

rules  |> kablebox()

# add vars from crosswalk 
rules %<>% left_join(crosswalk)

rules |> 
  #filter(regulationsdotgov_acronym == department_agency_acronym) |> 
  ungroup() |> 
  drop_na(regulationsdotgov_agency) |> 
  filter(rules_n > 100) |> 
  ggplot() + 
  aes(x = rules_n, 
      y = reorder(regulationsdotgov_agency, rules_n) ) + 
  geom_col() + 
  labs(x = "Proposed of Rules with Racial Words", 
       y = "")

rules |> 
  #filter(regulationsdotgov_acronym == department_agency_acronym) |> 
  filter(#rules_percent <= 1,
         rules_n > 100) |> #FIXME 
  ungroup() |> 
  drop_na(regulationsdotgov_agency) |> 
  #filter(rules_percent > .7500 | rules_percent < .2500 ) |> 
  ggplot() + 
  aes(x = rules_percent, 
      y = reorder(regulationsdotgov_agency, rules_percent) ) + 
  geom_col() + 
  labs(x = "Share of Rules with Racial Words", 
       y = "")
```

# Combined

```{r join}
d <- full_join(nyt,
               mfl) |> distinct() |> 
  full_join(rules |> select(department_agency_acronym, 
                            rules_percent, rules_percent_norm,
                            rules_n, rules_norm)) |> 
  distinct() |> 
  select(ends_with("norm"), everything())

d  |> kablebox()
```

"hist"

```{r}
#| fig-width: 2
#| fig-height: 1
#| layout-ncol: 2
#| label: hist


ggplot(d) +
  aes(x = MFL_norm) + 
  geom_histogram()

ggplot(d) +
  aes(x = MFL_percent_norm) + 
  geom_histogram()


ggplot(d) +
  aes(x = NYT_norm) + 
  geom_histogram()

ggplot(d) +
  aes(x = NYT_percent_norm) + 
  geom_histogram()

ggplot(d) +
  aes(x = rules_norm) + 
  geom_histogram()

ggplot(d) +
  aes(x = rules_percent_norm) + 
  geom_histogram()

```



## Comparing Racialization Measures

### nyt_v_mfl


```{r}
#| label: nyt_v_mfl
#| fig-width: 5
#| fig-height: 5
#| layout-ncol: 2

d1 <- drop_na(d, NYT_norm, MFL_norm)

max_x <- max_y <- max(c(d1$NYT_norm, d1$MFL_norm), na.rm = T)
min_x <- min_y <-  min(c(d1$MFL_norm, d1$NYT_norm), na.rm = T)


d1 |> 
  ggplot() + 
  aes(x = MFL_norm, 
      y = NYT_norm,
      label = department_agency_acronym |> str_remove(".*_")) + 
    geom_line(aes(y = MFL_norm), color = "red")  + 
  annotate(x = min_x, y = max_y, geom = "text", 
           label = 'More Racialized\nin NYT', color = "red", hjust = 0) + 
  annotate(x = max_x, y = min_y, geom = "text", 
           label = 'More Racialized\nin MFL', color = "red", hjust = 1) + 
  #geom_smooth(method = "lm") + 
  geom_point() +    geom_label_repel(size =3,force_pull = 10, alpha = .5)  + 
  labs(title = "Racialized Attention",
       x = "Scaled Mandate for Leadership (Project 2025) Mentions",
       y = "Scaled NYT Articles")


d1 <- drop_na(d, NYT_percent_norm, MFL_percent_norm)

max_x <- max(c(d1$MFL_percent_norm), na.rm = T)
max_y <- max(c(d1$MFL_percent_norm, d1$NYT_percent_norm), na.rm = T)
min_x <- min(c(d1$MFL_percent_norm), na.rm = T)
min_y <-  min(c(d1$MFL_percent_norm, d1$NYT_percent_norm), na.rm = T)

d1 |> 
  ggplot() + 
  aes(x = MFL_percent_norm, 
      y = NYT_percent_norm,
      label = department_agency_acronym |> str_remove(".*_")) + 
    geom_line(aes(y = MFL_percent_norm), color = "red")  + 
  annotate(x = min_x, y = max_y, geom = "text", 
           label = 'More Racialized\nin NYT', color = "red", hjust = 0) + 
  annotate(x = max_x, y = min_y, geom = "text", 
           label = 'More Racialized\nin MFL', color = "red", hjust = 1) +  
  # geom_smooth(method = "lm") + 
  geom_point() +    geom_label_repel(size =3,force_pull = 10, alpha = .5)  + 
  labs(title = "Racialized Attention as a Share of Total",
       x = "Scaled Share of Mandate for Leadership (Project 2025)",
       y = "Scaled Share of NYT Articles")


cor_nyt_v_mfl <- cor.test(d$MFL_percent_norm, d$NYT_percent_norm)


cor_nyt_v_mfl
```



### nyt_v_rules



```{r}
#| label: nyt_v_rules
#| fig-width: 5
#| fig-height: 5
#| layout-ncol: 2

d1 <- drop_na(d, NYT_norm, rules_norm)

max_x <- max_y <- max(c(d1$NYT_norm, d1$rules_norm), na.rm = T)
min_x <- min_y <-  min(c(d1$rules_norm, d1$NYT_norm), na.rm = T)

d1 |> 
  ggplot() + 
  aes(x = rules_norm, 
      y = NYT_norm,
      label = department_agency_acronym |> str_remove(".*_")) + 
    geom_line(aes(y = rules_norm), color = "red")  + 
  annotate(x = min_x, y = max_y, geom = "text", 
           label = 'More Racialized\nin NYT', color = "red", hjust = 0) + 
  annotate(x = max_x, y = min_y, geom = "text", 
           label = 'More Racialized\nin Rules', color = "red", hjust = 1) + 
  #geom_smooth(method = "lm") + 
  geom_point() +    geom_label_repel(size =3,force_pull = 10, alpha = .5)  + 
  labs(title = "Racialized Attention",
       x = "Scaled Rulemaking Mentions",
       y = "Scaled NYT Articles")

d1 <- drop_na(d, NYT_percent_norm, rules_percent_norm)

max_x <- max(c(d1$rules_percent_norm), na.rm = T)
max_y <- max(c(d1$NYT_percent_norm), na.rm = T)
min_x <- min_y <-  min(c(d1$rules_percent_norm, d1$NYT_percent_norm), na.rm = T)

d1 |> 
  ggplot() + 
  aes(x = rules_percent_norm, 
      y = NYT_percent_norm,
      label = department_agency_acronym |> str_remove(".*_")) + 
    geom_line(aes(y = rules_percent_norm), color = "red")  + 
  annotate(x = min_x, y = max_y, geom = "text", 
           label = 'More Racialized\nin NYT', color = "red", hjust = 0) + 
  annotate(x = max_x, y = min_y, geom = "text", 
           label = 'More Racialized\nin Rules', color = "red", hjust = 1) + 
  #geom_smooth(method = "lm") + 
  geom_point() +    geom_label_repel(size =3,force_pull = 10, alpha = .5)  + 
  labs(title = "Racialized Attention as a Share of Total",
       x = "Scaled Rulemaking Mentions",
       y = "Scaled NYT Articles")

cor_rules_v_nyt <- cor.test(d$rules_percent_norm, d$NYT_percent_norm)

cor_rules_v_nyt
```

### rules_v_mfl

```{r}
#| label: rules_v_mfl
#| fig-width: 5
#| fig-height: 5
#| layout-ncol: 2

d1 <- drop_na(d, MFL_norm, rules_norm)

max_x <- max_y <- max(c(d1$MFL_norm, d1$rules_norm), na.rm = T)
min_x <- min_y <-  min(c(d1$rules_norm, d1$NYT_norm), na.rm = T)

d1 |> 
  ggplot() + 
  aes(x = MFL_norm, 
      y = rules_norm,
      label = department_agency_acronym |> str_remove(".*_")) + 
    geom_line(aes(y = MFL_norm), color = "red")  + 
  annotate(x = min_x, y = max_y, geom = "text", 
           label = 'More Racialized\nin Rules', color = "red", hjust = 0) + 
  annotate(x = max_x, y = min_y, geom = "text", 
           label = 'More Racialized\nin MFL', color = "red", hjust = 1) + 
  #geom_smooth(method = "lm") + 
  geom_point() +    geom_label_repel(size =3,force_pull = 10, alpha = .5)  + 
  labs(title = "Racialized Attention",
       x = "Scaled Mandate for Leadership (Project 2025) Mentions",
       y = "Scaled Rulemaking Mentions")


d1 <- drop_na(d, MFL_percent_norm, rules_percent_norm)

max_x <- max_y <- max(c(d1$MFL_percent_norm, d1$rules_percent_norm), na.rm = T)
min_x <- min_y <-  min(c(d1$rules_percent_norm, d1$MFL_percent_norm), na.rm = T)



d1 |> 
  ggplot() + 
  aes(x = MFL_percent_norm, 
      y = rules_percent_norm,
      label = department_agency_acronym |> str_remove(".*_")) + 
    geom_line(aes(y = MFL_percent_norm), color = "red")  + 
  annotate(x = min_x, y = max_y, geom = "text", 
           label = 'More Racialized\nin Rules', color = "red", hjust = 0) + 
  annotate(x = max_x, y = min_y, geom = "text", 
           label = 'More Racialized\nin MFL', color = "red", hjust = 1) + 
  #geom_smooth(method = "lm") + 
  geom_point() +    geom_label_repel(size =3,force_pull = 10, alpha = .5)  + 
  labs(title = "Racialized Attention as a Share of Total",
       x = "Scaled Mandate for Leadership (Project 2025) Mentions",
       y = "Scaled Rulemaking Mentions")

cor_rules_v_mfl <- cor.test(d$MFL_percent_norm, d$rules_percent_norm)

cor_rules_v_mfl
```


## Combined Racialization Score


```{r}
d <- d |>
  group_by(department_agency_acronym) |>
  mutate(racialization = mean(c(MFL_percent_norm, 
                              NYT_percent_norm, 
                              rules_percent_norm),
                              trim = 0,
                              na.rm = TRUE))

d  |> 
  select(agency = department_agency_acronym, racialization, ends_with("percent_norm")) |>
  kablebox()
```

### Least racialized 
```{r}
d %>% distinct(department_agency_acronym, racialization) %>% 
  arrange(racialization) %>% kablebox()
```

### Most racialized

```{r}
d %>% distinct(department_agency_acronym, racialization) %>% 
  arrange(-racialization) %>% kablebox()
```


## Perceived Ideology 

```{r}
# from code/get_ideology_scores.R
load( here::here("data", "rcl_ideology_estimates.rda") )

rcl_ideology_estimates |> kablebox()

d <- d  |>  full_join(rcl_ideology_estimates)  |> 
  rename(perceived_ideology_estimate = X.ideo_rating.)  |> 
  distinct()  |> 
  add_count(department_agency_acronym) |> 
  distinct()

# d |> distinct() |>  count(department_agency_acronym, sort = T)

d %<>% drop_na(department_agency_acronym)
```

"ideo_v_score"

```{r}
#| label: ideo_v_score
#| fig-width: 6
#| fig-height: 5
#| layout-ncol: 1

max_y = max(d$racialization, na.rm = T)

d |> 
  ggplot() + 
  aes(x = perceived_ideology_estimate, 
      y = racialization,
      label = department_agency_acronym |> str_remove(".*_")) + 
    #geom_line(aes(y = perceived_ideology_estimate), color = "red")  + 
  annotate(x = 2, y = max_y, geom = "text", label = 'Racialized\n"Conservative"', color = "red", hjust = 1) + 
    annotate(x =-2, y = max_y, geom = "text", label = 'Racialized\n"Liberal"', color = "red", hjust = 0) + 
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
    geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
geom_smooth(method = "lm") + 
  #geom_smooth(method = "lm") + 
  geom_point() +    geom_label_repel(size =3,force_pull = 10, alpha = .5)  + 
  labs(title = "",
       x = "Perceived Ideological Leaning\n.     ← More Liberal                More Conservative →",
       y = "Racialization Score")



d |> 
  ggplot() + 
  aes(x = abs(perceived_ideology_estimate), 
      y = racialization,
      label = department_agency_acronym |> str_remove(".*_")) + 
    #geom_line(aes(y = perceived_ideology_estimate), color = "red")  + 
  geom_label_repel(size =3, force_pull = 10, alpha = .5)  + 
  annotate(x =0, y = max_y, geom = "text", label = 'Racialized\n"Moderate"', color = "red", hjust = 0) + 
    annotate(x =2, y = max_y, geom = "text", label = 'Racialized\n"Ideological"', color = "red", hjust = 1) + 
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
    geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
geom_smooth(method = "lm") + 
  #geom_smooth(method = "lm") + 
  geom_point() +    
  labs(title = "",
       x = "Perceived Ideological Distance from Center",
       y = "Racialization Score")
```


### Ideology v Project 2025 

"ideo_v_mfl"

```{r}
#| label: ideo_v_mfl
#| fig-width: 5
#| fig-height: 5
#| layout-ncol: 2

max_y = max(d$MFL_norm, na.rm = T)

d |> 
  ggplot() + 
  aes(x = perceived_ideology_estimate, 
      y = MFL_norm,
      label = department_agency_acronym |> str_remove(".*_")) + 
    #geom_line(aes(y = perceived_ideology_estimate), color = "red")  + 
  geom_label_repel(size =3,force_pull = 10, alpha = .5)  + 
  annotate(x =2, y = max_y, geom = "text", 
           label = 'Racialized\n"Conservative"', color = "red", hjust = 1) + 
    annotate(x =-2, y = max_y, geom = "text", 
             label = 'Racialized\n"Liberal"', color = "red", hjust = 0) +   #geom_smooth(method = "lm") + 
  geom_point() +    
  
  labs(title = "Racialized Attention",
       x = "Perceived Ideological Leaning\n.     ← More Liberal                More Conservative →",
       y = "Count of Racialized Terms in Project 2025")

max_y = max(d$MFL_percent_norm, na.rm = T)


d |> 
  ggplot() + 
  aes(x = perceived_ideology_estimate, 
      y = MFL_percent_norm,
      label = department_agency_acronym |> str_remove(".*_")) + 
  geom_label_repel(size =3,force_pull = 10, alpha = .5)  + 
    #geom_line(aes(y = perceived_ideology_estimate), color = "red")  + 
  annotate(x =2, y =max_y, geom = "text", label = 'Racialized\n"Conservative"', color = "red", hjust = 1) + 
    annotate(x =-2, y =max_y, geom = "text", label = 'Racialized\n"Liberal"', color ="red", hjust = 0) +   # geom_smooth(method = "lm") + 
  geom_point() +    
  labs(title = "Racialized Attention as a Share of Total",
       x = "Perceived Ideological Leaning\n.     ← More Liberal                More Conservative →",
       y = "Racialized Share of Project 2025 Sentences")

```


### Ideology v NYT 

"ideo_v_nyt"

```{r}
#| label: ideo_v_nyt
#| fig-width: 5
#| fig-height: 5
#| layout-ncol: 2

max_y = max(d$NYT_percent_norm, na.rm = T)

d |> 
  ggplot() + 
  aes(x = perceived_ideology_estimate, 
      y = NYT_norm,
      label = department_agency_acronym |> str_remove(".*_")) + 
    geom_label_repel(size =3,force_pull = 10, alpha = .5)  + 
    #geom_line(aes(y = perceived_ideology_estimate), color = "red")  + 
  annotate(x =2, y= max_y, geom = "text", 
           label = 'Racialized\n"Conservative"', color = "red", hjust = 1) + 
    annotate(x =-2, y = max_y, geom = "text", 
             label = 'Racialized\n"Liberal"', color = "red", hjust = 0) +   #geom_smooth(method = "lm") + 
  geom_point() +    
  labs(title = "Racialized Attention",
       x = "Perceived Ideological Leaning\n.     ← More Liberal                More Conservative →",
       y = "NYT Articles with Racial Language")

max_y = max(d$NYT_percent_norm, na.rm = T)

d |> 
  ggplot() + 
  aes(x = perceived_ideology_estimate, 
      y = NYT_percent_norm,
      label = department_agency_acronym |> str_remove(".*_")) + 
   geom_label_repel(size =3,force_pull = 10, alpha = .5)  + 
    #geom_line(aes(y = perceived_ideology_estimate), color = "red")  + 
  annotate(x =2, y = max_y, geom = "text", label = 'Racialized\n"Conservative"', color = "red", hjust = 1) + 
    annotate(x =-2, y = max_y, geom = "text", label = 'Racialized\n"Liberal"', color = "red", hjust = 0) +   # geom_smooth(method = "lm") + 
  geom_point() +   
  labs(title = "Racialized Attention as a Share of Total",
       x = "Perceived Ideological Leaning\n.     ← More Liberal                More Conservative →",
       y = "Share of NYT Articles with Racial Language")

```

### Ideology v Rulemaking 

"ideo_v_rules"

```{r}
#| label: ideo_v_rules
#| fig-width: 5
#| fig-height: 5
#| layout-ncol: 2

max_y = max(d$rules_norm, na.rm = T)

d |> 
  ggplot() + 
  aes(x = perceived_ideology_estimate, 
      y = rules_norm,
      label = department_agency_acronym |> str_remove(".*_")) + 
    geom_label_repel(size =3,force_pull = 10, alpha = .5)  + 
    #geom_line(aes(y = perceived_ideology_estimate), color = "red")  + 
  annotate(x =2, y= max_y, geom = "text", 
           label = 'Racialized\n"Conservative"', color = "red", hjust = 1) + 
    annotate(x =-2, y = max_y, geom = "text", 
             label = 'Racialized\n"Liberal"', color = "red", hjust = 0) +   #geom_smooth(method = "lm") + 
  geom_point() +    
  labs(title = "Racialized Attention",
       x = "Perceived Ideological Leaning\n.     ← More Liberal                More Conservative →",
       y = "Rules with Racial Language")


# PERCENT 
max_y = max(d$rules_percent_norm, na.rm = T)

d |>
  ggplot() +
  aes(x = perceived_ideology_estimate,
      y = rules_percent_norm,
      label = department_agency_acronym |> str_remove(".*_")) +
  geom_label_repel(size =3,force_pull = 10, alpha = .5)  +
    #geom_line(aes(y = perceived_ideology_estimate), color = "red")  +
  annotate(x =2, y = max_y, geom = "text", label = 'Racialized\n"Conservative"', color = "red", hjust = 1) +
    annotate(x =-2, y = max_y, geom = "text", label = 'Racialized\n"Liberal"', color = "red", hjust = 0) +   # geom_smooth(method = "lm") +
  geom_point() +    
  labs(title = "Racialized Attention as a Share of Total",
       x = "Perceived Ideological Leaning\n.     ← More Liberal                More Conservative →",
       y = "Share of Rules with Racial Language")

```


# Correlations

```{r}
# COMBINED 
cor_ido <- cor.test(d$racialization, d$perceived_ideology_estimate)
cor_ido 
cor_ido_abs <- cor.test(d$racialization, abs(d$perceived_ideology_estimate))
cor_ido_abs

# MFL
cor_ido_mfl <- cor.test(d$MFL_percent_norm, d$perceived_ideology_estimate)
cor_ido_mfl
cor_ido_mfl_abs <-cor.test(d$MFL_percent_norm, abs(d$perceived_ideology_estimate))
cor_ido_mfl_abs

# NYT
cor_ido_nyt <-cor.test(d$NYT_percent_norm, d$perceived_ideology_estimate)
cor_ido_nyt 
cor_ido_nyt_abs <-cor.test(d$NYT_percent_norm, abs(d$perceived_ideology_estimate))
cor_ido_nyt_abs

# Rules 
cor_ido_rules <-cor.test(d$rules_percent_norm,  d$perceived_ideology_estimate)
cor_ido_rules
cor_ido_rules_abs <-cor.test(d$rules_percent_norm, abs(d$perceived_ideology_estimate))
cor_ido_rules_abs
```



```{r save}
save(#correlations 
  cor_nyt_v_mfl, 
  cor_rules_v_mfl,
  cor_rules_v_nyt,
  cor_ido,
  cor_ido_abs,
  cor_ido_mfl,
  cor_ido_mfl_abs,
  cor_ido_nyt,
  cor_ido_nyt_abs,
  cor_ido_rules,
  cor_ido_rules_abs,
  # n MFL
     n_mfl_racial,
n_mfl_total,
n_mfl_agencies, 
# NYT 
     n_nyt_articles,
n_nyt_racial,
     n_nyt_agencies,
# Rules 
n_rules,
     n_rules_racial,
     n_rules_agencies, 
# path
     file = here::here("data", "numbers-for-paper.Rdata"))
```



# DOGE Layoff data from Adam Bonica 

"doge"

```{r}
#| label: doge
#| fig-width: 7
#| fig-height: 5
#| layout-ncol: 2

# from get_data_bonica.R
load(here::here("data", "bonica.rda"))

names(bonica)<-names(bonica) |> tolower()


bonica<-bonica |> 
  mutate(doge_layoffs= as.logical(doge_layoffs),
         targeted_for_dismantling= as.logical(targeted_for_dismantling))  |> 
  mutate(agency = department_agency_acronym |> str_remove("_.*"))

doge_plot <- function(data){
  
  data |> 
  filter(total_staff>1000) |> #, total_staff<10^6)
#create scatter plot with vertical line at zero perceived ideology  
ggplot() +
       aes(x = perceived_ideology_estimate, 
           y = total_staff) +
  # Add grid lines
  geom_hline(yintercept = c(1000, 10000, 100000, 1000000), 
             color = "gray90", linetype = "dashed") +
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
  # Add agency acronyms colored according to DOGE layoff variable
  geom_text_repel(aes(label = agency,
                color = doge_layoffs), 
            size=3)+ 
  # Scale transformations
  scale_y_log10(breaks = c(1000, 10000, 100000, 1000000),
                labels = scales::comma) +
  scale_x_continuous(breaks = seq(-2, 2, 1)) +
  theme_minimal()+
  theme(
      plot.title = element_text(face = "bold", size = 16),
      plot.subtitle = element_text(size = 14),
      plot.caption = element_text(size = 10, hjust = 0))+
  # Custom colors
  # scale_color_manual(values = c("gray60", "red"),
  #                    name = "Layoff Status",
  #                    labels = c("No Layoffs", "Layoffs")) +
  # Labels
  labs(title = "Empirical Evidence of Ideological Targeting",
       subtitle = "Agencies seen as liberal are significantly more likely to face layoffs.",
       x = "Perceived Ideological Leaning\n(← More Liberal | More Conservative →)",
       y = "Agency Size (Number of Staff)",
       color = "DOGE Layoffs",
       caption = "Note: Analysis includes only agencies with 500+ staff members. Ideology estimates are based on survey responses from 1,500+ federal executives rating agencies
policy views as liberal to conservative across both Democratic and Republican administrations.
Source: Richardson, Clinton, & Lewis (2018). Elite Perceptions of Agency Ideology and Workforce Skill. The Journal of Politics 80(1).") 
} 


doge_plot(bonica |> mutate(agency = department_agency_acronym) )

# summarized at dep level 
doge_plot(bonica |> group_by(agency) |> 
            summarise(perceived_ideology_estimate = mean(perceived_ideology_estimate),
                      total_staff = sum(total_staff),
                      annual_budget_usd = sum(annual_budget_usd),
                      doge_layoffs = sum(doge_layoffs) >0 ))




# 
# b2 <- bonica |> group_by(agency) |> 
#             summarise(perceived_ideology_estimate = mean(perceived_ideology_estimate),
#                       total_staff = sum(total_staff),
#                       annual_budget_usd = sum(annual_budget_usd),
#                       doge_layoffs = ifelse(sum(doge_layoffs) >0, "Targeted", "Not Targeted" ))

b <- bonica |> mutate(doge_layoffs = ifelse(doge_layoffs >0, "Targeted", "Not Targeted" )) |> 
  mutate(dog_layoffs = replace_na(doge_layoffs, "No Data")) |> 
  rename(perceived_ideology_estimate_bonica = perceived_ideology_estimate) 

if(testing){
  anti_join(b, d) |> distinct(agency, department_agency_acronym)  # in bonica, not in our data
anti_join(d, b)  |> distinct(agency, department_agency_acronym)# in our data, not in bonica
} 
```

### "by_staff"

```{r}
#| fig-width: 6
#| fig-height: 3
#| layout-ncol: 2
#| label: by_staff

d %<>% full_join(b)

# NYT by staff an layoffs 
ggplot(d) +
       aes(x = NYT_percent_norm, 
           y = total_staff) +
  # Add grid lines
  geom_hline(yintercept = c(1000, 10000, 100000, 1000000), 
             color = "gray90", linetype = "dashed") +
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
  # Add agency acronyms colored according to DOGE layoff variable
  geom_text_repel(aes(label = department_agency_acronym |> str_remove(".*_"),
                color = doge_layoffs), 
            size=3)+ 

  # Scale transformations
  scale_y_log10(breaks = c(1000, 10000, 100000, 1000000),
                labels = scales::comma) +
  scale_x_continuous(breaks = seq(-2, 2, 1)) +
  labs(title = "",
       x = "Number of NYT Articles\n.     ← Less Racialized                More Racialized →",
       y = "Staff",
       color = "Layoffs")


# PROJECT 2025 by staff and layoffs 
ggplot(d) +
       aes(x = MFL_percent_norm, 
           y = total_staff) +
  # Add grid lines
  geom_hline(yintercept = c(1000, 10000, 100000, 1000000), 
             color = "gray90", linetype = "dashed") +
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
  # Add agency acronyms colored according to DOGE layoff variable
  geom_text_repel(aes(label = department_agency_acronym |> str_remove(".*_"),
                color = doge_layoffs), 
            size=3)+ 

  # Scale transformations
  scale_y_log10(breaks = c(1000, 10000, 100000, 1000000),
                labels = scales::comma) +
  scale_x_continuous(breaks = seq(-2, 2, 1)) +
  labs(title = "",
       x = "Share of NYT Articles\n.     ← Less Racialized                More Racialized →",
       y = "Staff",
       color = "Layoffs")



# Rules by staff and layoffs 
ggplot(d) +
       aes(x = rules_norm, 
           y = total_staff) +
  # Add grid lines
  geom_hline(yintercept = c(1000, 10000, 100000, 1000000), 
             color = "gray90", linetype = "dashed") +
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
  # Add agency acronyms colored according to DOGE layoff variable
  geom_text_repel(aes(label = department_agency_acronym |> str_remove(".*_"),
                color = doge_layoffs), 
            size=3)+ 
  # Scale transformations
  scale_y_log10(breaks = c(1000, 10000, 100000, 1000000),
                labels = scales::comma) +
  scale_x_continuous(breaks = seq(-2, 2, 1)) +
  labs(title = "",
       x = "Racial Language in Rules\n.     ← Less Racialized                More Racialized →",
       y = "Staff",
       color = "Layoffs")



# Rules by staff and layoffs 
ggplot(d) +
       aes(x = rules_percent_norm, 
           y = total_staff) +
  # Add grid lines
  geom_hline(yintercept = c(1000, 10000, 100000, 1000000), 
             color = "gray90", linetype = "dashed") +
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
  # Add agency acronyms colored according to DOGE layoff variable
  geom_text_repel(aes(label = department_agency_acronym |> str_remove(".*_"),
                color = doge_layoffs), 
            size=3)+ 
  # Scale transformations
  scale_y_log10(breaks = c(1000, 10000, 100000, 1000000),
                labels = scales::comma) +
  scale_x_continuous(breaks = seq(-2, 2, 1)) +
  labs(title = "",
       x = "Share of Racial Language in Rules\n.     ← Less Racialized                More Racialized →",
       y = "Staff",
       color = "Layoffs")
```

#### By Racialization Score

"ideo_v_racialization_layoffs"

```{r}
#| label: ideo_v_racialization_layoffs
#| fig-width: 6
#| fig-height: 3
#| layout-ncol: 2

ggplot(d) +
       aes(x = perceived_ideology_estimate, 
           y = racialization) +
  # Add grid lines
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
    geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
#geom_smooth(method = "lm") + 
  # Add agency acronyms colored according to DOGE layoff variable
  geom_text_repel(aes(label = department_agency_acronym |> str_remove(".*_"),
                color = doge_layoffs), 
            size=3)+ 

  # Scale transformations
  scale_x_continuous(breaks = seq(-2, 2, 1)) + 
  labs(title = "",
       x = "Perceived Ideological Leaning\n.     ← More Liberal                More Conservative →",
       y = "Racialization Score",
       color = "Layoffs")


ggplot(d) +
       aes(x = abs(perceived_ideology_estimate), 
           y = racialization) +
  # Add grid lines
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
    geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
#geom_smooth(method = "lm") + 
  # Add agency acronyms colored according to DOGE layoff variable
  geom_text_repel(aes(label = department_agency_acronym |> str_remove(".*_"),
                color = doge_layoffs), 
            size=3)+ 
  # Scale transformations
  scale_x_continuous(breaks = seq(-2, 2, 1)) + 
  labs(title = "",
       x = "Perceived Ideological Leaning\n.     ← More Moderate                More Extreme →",
       y = "Racialization Score",
       color = "Layoffs")

```

#### By Project 2025 Racialization 


"ideo_v_mfl_layoffs"

```{r}
#| label: ideo_v_mfl_layoffs
#| fig-width: 6
#| fig-height: 3
#| layout-ncol: 2

ggplot(d) +
       aes(x = perceived_ideology_estimate, 
           y = MFL_percent_norm) +
  # Add grid lines
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
    geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
# geom_smooth(method = "lm") + 
  # Add agency acronyms colored according to DOGE layoff variable
  geom_text_repel(aes(label = department_agency_acronym |> str_remove(".*_"),
                color = doge_layoffs), 
            size=3)+ 

  # Scale transformations
  scale_x_continuous(breaks = seq(-2, 2, 1)) + 
  labs(title = "",
       x = "Perceived Ideological Leaning\n.     ← More Liberal                More Conservative →",
       y = "MFL Percent Racialization Score",
       color = "Layoffs")


ggplot(d) +
       aes(x = perceived_ideology_estimate, 
           y = MFL_norm) +
  # Add grid lines
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
    geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
#geom_smooth(method = "lm") + 
  # Add agency acronyms colored according to DOGE layoff variable
  geom_text_repel(aes(label = department_agency_acronym |> str_remove(".*_"),
                color = doge_layoffs), 
            size=3)+ 
  # Scale transformations
  scale_x_continuous(breaks = seq(-2, 2, 1)) + 
  labs(title = "",
       x = "Perceived Ideological Leaning\n.     ← More Liberal                More Conservative →",
       y = "MFL Racialization Score",
       color = "Layoffs")


ggplot(d) +
       aes(x = abs(perceived_ideology_estimate), 
           y = MFL_percent_norm) +
  # Add grid lines
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
    geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
#geom_smooth(method = "lm") + 
  # Add department_agency_acronym acronyms colored according to DOGE layoff variable
  geom_text_repel(aes(label = department_agency_acronym |> str_remove(".*_"),
                color = doge_layoffs), 
            size=3)+ 
  # Scale transformations
  scale_x_continuous(breaks = seq(-2, 2, 1)) + 
    labs(title = "",
       x = "Perceived Ideological Leaning\n.     ← More Moderate                More Extreme →",
       y = "MFL Percent Racialization Score",
       color = "Layoffs")


ggplot(d) +
       aes(x = abs(perceived_ideology_estimate), 
           y = MFL_norm) +
  # Add grid lines
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
    geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
#geom_smooth(method = "lm") + 
  # Add department_agency_acronym acronyms colored according to DOGE layoff variable
  geom_text_repel(aes(label = department_agency_acronym |> str_remove(".*_"),
                color = doge_layoffs), 
            size=3)+ 
  # Scale transformations
  scale_x_continuous(breaks = seq(-2, 2, 1)) + 
    labs(title = "",
       x = "Perceived Ideological Leaning\n.     ← More Moderate                More Extreme →",
       y = "MFL Racialization Score",
       color = "Layoffs")

```


#### By Rulemaking Racialization 


"ideo_v_rules_layoffs"

```{r}
#| label: ideo_v_rules_layoffs
#| fig-width: 6
#| fig-height: 3
#| layout-ncol: 2

ggplot(d) +
       aes(x = perceived_ideology_estimate, 
           y = rules_norm) +
  # Add grid lines
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
    geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
# geom_smooth(method = "lm") + 
  # Add agency acronyms colored according to DOGE layoff variable
  geom_text_repel(aes(label = department_agency_acronym |> str_remove(".*_"),
                color = doge_layoffs), 
            size=3)+ 
  # Scale transformations
  scale_x_continuous(breaks = seq(-2, 2, 1)) + 
    labs(title = "",
       x = "Perceived Ideological Leaning\n.     ← More Liberal                More Conservative →",
       y = "Rulemaking Racialization Score",
       color = "Layoffs")

ggplot(d) +
       aes(x = abs(perceived_ideology_estimate), 
           y = rules_norm) +
  # Add grid lines
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
    geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
# geom_smooth(method = "lm") + 
  # Add department_agency_acronym acronyms colored according to DOGE layoff variable
  geom_text_repel(aes(label = department_agency_acronym |> str_remove(".*_"),
                color = doge_layoffs), 
            size=3)+ 
  # Scale transformations
  scale_x_continuous(breaks = seq(-2, 2, 1)) + 
  labs(title = "Perceived Extremeism and Racialized Attention Share")

# PERCENT 
ggplot(d) +
       aes(x = perceived_ideology_estimate, 
           y = rules_percent_norm) +
  # Add grid lines
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
    geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
# geom_smooth(method = "lm") + 
  # Add agency acronyms colored according to DOGE layoff variable
  geom_text_repel(aes(label = department_agency_acronym |> str_remove(".*_"),
                color = doge_layoffs), 
            size=3)+ 
  # Scale transformations
  scale_x_continuous(breaks = seq(-2, 2, 1)) + 
    labs(title = "",
       x = "Perceived Ideological Leaning\n.     ← More Liberal                More Conservative →",
       y = "Rulemaking Percent Racialization Score",
       color = "Layoffs")

ggplot(d) +
       aes(x = abs(perceived_ideology_estimate), 
           y = rules_percent_norm) +
  # Add grid lines
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
    geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
# geom_smooth(method = "lm") + 
  # Add department_agency_acronym acronyms colored according to DOGE layoff variable
  geom_text_repel(aes(label = department_agency_acronym |> str_remove(".*_"),
                color = doge_layoffs), 
            size=3)+ 
  # Scale transformations
  scale_x_continuous(breaks = seq(-2, 2, 1)) + 
    labs(title = "",
       x = "Perceived Ideological Leaning\n.     ← More Moderate                More Extreme →",
       y = "Rulemaking Racialization Score",
       color = "Layoffs")
```

#### By NYT Racialization 

"ideo_v_nyt_layoffs"

```{r}
#| label: ideo_v_nyt_layoffs
#| fig-width: 6
#| fig-height: 3
#| layout-ncol: 2

ggplot(d) +
       aes(x = perceived_ideology_estimate, 
           y = NYT_percent_norm) +
  # Add grid lines
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
    geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
#geom_smooth(method = "lm") + 
  # Add department_agency_acronym acronyms colored according to DOGE layoff variable
  geom_text_repel(aes(label = department_agency_acronym |> str_remove(".*_"),
                color = doge_layoffs), 
            size=3)+ 
  # Scale transformations
  scale_x_continuous(breaks = seq(-2, 2, 1)) + 
    labs(title = "",
       x = "Perceived Ideological Leaning\n.     ← More Liberal                More Conservative →",
       y = "NYT Percent Racialization Score",
       color = "Layoffs")


ggplot(d) +
       aes(x = perceived_ideology_estimate, 
           y = NYT_norm) +
  # Add grid lines
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
    geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
#geom_smooth(method = "lm") + 
  # Add department_agency_acronym acronyms colored according to DOGE layoff variable
  geom_text_repel(aes(label = department_agency_acronym |> str_remove(".*_"),
                color = doge_layoffs), 
            size=3)+ 
  # Scale transformations
  scale_x_continuous(breaks = seq(-2, 2, 1)) + 
    labs(title = "",
       x = "Perceived Ideological Leaning\n.     ← More Liberal                More Conservative →",
       y = "NYT Racialization Score",
       color = "Layoffs")

ggplot(d) +
       aes(x = abs(perceived_ideology_estimate), 
           y = NYT_percent_norm) +
  # Add grid lines
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
    geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
#geom_smooth(method = "lm") + 
  # Add department_agency_acronym acronyms colored according to DOGE layoff variable
  geom_text_repel(aes(label = department_agency_acronym |> str_remove(".*_"),
                color = doge_layoffs), 
            size=3)+ 
  # Scale transformations
  scale_x_continuous(breaks = seq(-2, 2, 1)) + 
    labs(title = "",
       x = "Perceived Ideological Leaning\n.     ← More Moderate                More Extreme →",
       y = "NYT Racialization Score",
       color = "Layoffs")


ggplot(d) +
       aes(x = abs(perceived_ideology_estimate), 
           y = NYT_norm) +
  # Add grid lines
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
    geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
#geom_smooth(method = "lm") + 
  # Add department_agency_acronym acronyms colored according to DOGE layoff variable
  geom_text_repel(aes(label = department_agency_acronym |> str_remove(".*_"),
                color = doge_layoffs), 
            size=3)+ 
  # Scale transformations
  scale_x_continuous(breaks = seq(-2, 2, 1)) + 
    labs(title = "",
       x = "NYT Perceived Ideological Leaning\n.     ← More Moderate                More Extreme →",
       y = "Racialization Score",
       color = "Layoffs")
```


"m_layoffs.Rdata"

```{r models}

d %<>% mutate(layoffs = doge_layoffs == "Targeted" )

#reproduce Adam's linear probability model 
m_layoffs_ido <-glm(layoffs ~ perceived_ideology_estimate + 
                  log(total_staff) + 
                  log(annual_budget_usd),
                  family=binomial(link="logit"),
                data=d )

# add MFL
m_layoffs_ideo_mfl <-glm(layoffs ~ perceived_ideology_estimate + 
                  #NYT_norm +
                 MFL_percent_norm +
                  log(total_staff) + 
                  log(annual_budget_usd),
                  family=binomial(link="logit"),
                data=d )

#reproduce Adam's linear probability model 
m_layoffs_mfl <- glm(layoffs ~ # perceived_ideology_estimate + 
                  #NYT_norm +
                 MFL_percent_norm +
                  log(total_staff) + 
                  log(annual_budget_usd),
                  family=binomial(link="logit"),
                data=d )

#reproduce Adam's linear probability model 
m_layoffs_ideo_mfl0 <-glm(layoffs ~ 
                          perceived_ideology_estimate*(MFL_n>10) +
                  log(total_staff) + 
                  log(annual_budget_usd),
                  family=binomial(link="logit"),
                data=d )


#display results 
library(modelsummary)

m_layoffs <- list(
  "(1)" = m_layoffs_ido ,
   "(2)" =  m_layoffs_ideo_mfl,
 "(3)" = m_layoffs_mfl ,
 "(4)" = m_layoffs_ideo_mfl0 
)
  
rows <- tibble(
  term = c("Dependent variable"),
   `(1)` = c("Layoffs") ,
   `(2)` = c("Layoffs") ,
  `(3)`= c("Layoffs"),
    `(4)`= c("Layoffs") 

)


modelsummary::modelsummary(m_layoffs, notes = "", stars = T)

save(m_layoffs, cm, rows, 
     file = here::here("models", "m_layoffs.Rdata"))
```

## Predictions 
"predictions"

```{r}
#| label: predictions
#| fig-width: 6
#| fig-height: 4

values <- tidyr::expand(d, 
                        total_staff = 100000,
                        annual_budget_usd = 5000000000,
                        #MFL_percent_norm,
                        MFL_n,
                        perceived_ideology_estimate)

predicted <- predictions(m_layoffs_ideo_mfl0, 
                         newdata = values)

predicted %>%  
  drop_na(MFL_n) %>% 
  ggplot() + 
  aes(x = perceived_ideology_estimate, 
      y = estimate, # predicted, 
      ymin = conf.low,# predicted - 1.96*std.error,
      ymax = conf.high, 
      color = MFL_n>10
      ) + 
  geom_pointrange(alpha = .5) + 
  labs(y = "Predicted Probability of Layoff",
       color = ">10 Racialized Words\nin Project 2025 MFL",
              x = "Perceived Ideological Leaning\n.     ← More Liberal                More Conservative →")
```

