---
title: "Words in Federal Policy"
format:
    html: 
      toc: true
      code-fold: true
editor_options: 
  chunk_output_type: console
---


```{r global.options, include=FALSE}
testing = F

library(tidyverse)
library(magrittr)
library(knitr)
library(kableExtra)
library(here)
library(scales)



knitr::opts_chunk$set(echo = T, # code is folded 
                      cache = T, # CACHE 
                      fig.width = 6.5, 
                      fig.height = 6.5,
                      split = T,
                      fig.align = 'center', 
                      fig.path='figs/',
                      fig.retina = 6,
                      warning = F, 
                      message = F)

# inline numbers round to 2, comma at thousands
inline <- function(x) {
  if (is.na(as.numeric(x))) {
    return (x)
    } else
        return (as.numeric(x) |> 
                 round(2) |>
                 format(big.mark=",") 
        )
}

knitr::knit_hooks$set(inline = inline)

# plot defaults 
library(ggplot2); theme_set(
      theme_minimal() + 
        theme(
          # # FOR AJPS
          # panel.grid = element_blank(),
          # legend.position = "bottom",
          # # END FOR AJPS 
          panel.border  = element_blank(),
          panel.grid.major.x = element_blank())
                            )
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
  scale_color_discrete <- function(...)
    scale_color_viridis_d(..., option = "inferno", begin = .2, end = .8, direction = 1)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(..., option = "inferno", begin = .2, end = .8, direction = 1)
  
# html table formatting
kablebox <- . %>%  
  head(100) %>%
  knitr::kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "200px")

kablebox_long <- . %>% 
  head(100) %>% 
  knitr::kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "500px")

int_breaks <- function(x, n = 5) {
  l <- pretty(x, n)
  l[abs(l %% 1) < .Machine$double.eps ^ 0.5] 
}
```




# All racialized terms 

```{r}
#| fig-width: 6
#| fig-height: 4
#| label: trends-rule-docs


load(here::here("data", "rules_terms.rda"))
terms |> kablebox()

load(here::here("data", "rules_racial_distinct.rda"))

set <- rules_racial_distinct  |>  #comments |>
  mutate(year = str_sub(postedDate, 1,4) |> as.numeric()) |> 
  filter(year > 2004) |> 
  #  filter(documentType %in% c("Rule", "Proposed Rule") ) |> 
  expand(agencyId, year, documentType)

df <- rules_racial_distinct  |>  #comments |>
  mutate(year = str_sub(postedDate, 1,4) |> as.numeric()) |>
  #filter(documentType %in% c("Rule", "Proposed Rule") ) |> 
  count(agencyId, year, documentType) |>
  group_by(agencyId) |>
  mutate(perAgency = sum(n)) |>
    full_join(set) |> 
  mutate(perAgency = replace_na(perAgency, 0)) |> 
    mutate(n = replace_na(n, 0)) |> 
  mutate(president = case_when(
    year < 2009 ~ "Bush",
    year > 2008 & year < 2017 ~ "Obama",
    year > 2016 & year < 2021 ~  "Trump",
    year > 2020 & year < 2025 ~ "Biden",
    year > 2024 & year < 2029 ~ "Trump2"
  ))

top <- df |> 
 # filter(agencyId != "FAA") |> #FIXME 
ungroup() |> 
  arrange(-perAgency) |> 
  distinct(agencyId, perAgency) |> 
  slice_max(perAgency, n = 4)

# facet by agency 
df |>
  drop_na(n) |> 
  filter(agencyId %in% top$agencyId,
         year > 2004,
         year < 2026) |>
  ggplot() +
  aes(x = year, 
      y = n, 
      color = president,
      shape = documentType) +
  geom_point() +
  labs(title = paste0('Policy Documents with Racialized Terms'),
       y = "Policy Documents",
       x = "",
       color = "") +
  geom_line() + 
  #geom_smooth(#method = "lm", se = F) +
  facet_wrap("agencyId",
             scales = "free_y") + 
  scale_color_viridis_d(option = "inferno", end = .8) + 
 scale_y_continuous(limits = c(0, NA)) + 
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45))

# facet by document type
df |>
  drop_na(n) |> 
  filter(agencyId %in% top$agencyId,
         year > 2004,
         year < 2026) |>
  mutate(documentType = str_remove(documentType, " M.*") ) |> 
  group_by(year, president, documentType) |>
  summarise(n = sum(n) ) |> 
  ggplot() +
  aes(x = year, 
      y = n, 
      color = president) +
  geom_point() +
  labs(title = paste0('Policy Documents with Racialized Terms'),
       y = "Policy Documents",
       x = "",
       color = "") +
  geom_line() + 
  #geom_smooth(#method = "lm", se = F) +
  facet_wrap("documentType",
             scales = "free_y") + 
  scale_color_viridis_d(option = "inferno", end = .8) + 
 scale_y_continuous(limits = c(0, NA)) + 
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45))
```



```{r}
#| fig-width: 5
#| fig-height: 4
#| label: trends-rule-docs-term


directory <- here::here("data", "search") |> str_replace("racialization", "regulationsdotgov-data")



# term <- terms[1]

p <- function(term){
  
    print(term)

path <- here::here(directory, term, paste0(term, "_documents.rda")) |> str_remove("racialization")

file.info(path) |> as_tibble()
load(path)

df <- documents |>  #comments |>
    #filter(documentType %in% c("Rule", "Proposed Rule") ) |> 
  mutate(year = str_sub(postedDate, 1,4) |> as.numeric()) |>
  count(agencyId, year) |>
  group_by(agencyId) |>
  mutate(perAgency = sum(n)) |>
  full_join(set) |> 
  mutate(perAgency = replace_na(perAgency, 0)) |> 
    mutate(n = replace_na(n, 0)) |> 
  mutate(president = case_when(
    year < 2009 ~ "Bush",
    year > 2008 & year < 2017 ~ "Obama",
    year > 2016 & year < 2021 ~  "Trump",
    year > 2020 & year < 2025 ~ "Biden",
    year > 2024 & year < 2029 ~ "Trump2"
  ))

unique(df$president)

filter(df, is.na(president))

top <- df |> 
ungroup() |> 
  filter(year > 2018) |> 
  arrange(-perAgency) |> 
  distinct(agencyId, perAgency) |> 
  slice_max(perAgency, n = 4, with_ties = F)

# if theres are agencies with data 
if(nrow(top)>1){
df |>
  drop_na(n) |> 
  filter(agencyId %in% top$agencyId,
         year > 2004,
         year < 2026) |>
  ggplot() +
  aes(x = year, 
      y = n, 
      color = president) +
  geom_point() +
  labs(title = paste0('Policy Documents with "', str_to_title(term), '"'),
       y = "Policy Documents",
       x = "",
       color = "") +
  geom_line() + 
  #geom_smooth(#method = "lm", se = F) +
  facet_wrap("agencyId",
             scales = "free_y") + 
  scale_color_viridis_d(option = "inferno", end = .8) + 
 scale_y_continuous(breaks = int_breaks, limits = c(0, NA)) + 
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45))

} else{
  ggplot(data.frame(1), aes(x=1)) + geom_histogram()
}
}


# ALL TERMS 
map(terms, possibly(p))

```



# Race

```{r trends-rule-docs-racial}
#| fig-width: 4
#| fig-height: 3

"Racial"|> p()                                 
"Racism"|> p()                                 
"Racist"|> p() 
"Gang"|> p()
# "Terrorist" |> p() 
"White Privilege"|> p() 
"Colorblindness" |> p()   
"Critical Race Theory"|> p()                                      
 
```

## Racialized Policy

### Civil Rights

```{r trends-rule-docs-civil-rights}
#| fig-width: 4
#| fig-height: 3


"Affirmative Action" |> p() 
"Civil Rights" |> p()           
"Diversity, equity"|> p() 
"Meritocracy"|> p() 
"Slavery"|> p()                                
```

### Immigration 

```{r trends-rule-docs-immigration}
#| fig-width: 4
#| fig-height: 3


"Immigration"|> p() 
"Citizenship"|> p() 
"Undocumented"|> p()                                                
"DACA" |> p() 
"Illegal Alien" |> p()                         
"Immigrant" |> p()                              
                      
"Secure the border"|> p() 
# "Border security" |> p()
"Border Crisis"|> p()
"Mexican Cartel" |> p()
# "Unaccompanied Alien Childen" |> p()
"Secure Border"|> p()
"Drug Cartel" |> p()


```

## Racial/Ethnic Groups

```{r trends-rule-docs-groups}
#| fig-width: 4
#| fig-height: 3


"Ethnicity" |> p() 
"Asian American" |> p() 
"Arab American" |> p() 
 "Black american" |> p() 
 "African American" |> p()   
 "Hispanic" |> p() 
 "latina" |> p() 
 "latino" |> p() 
 "MENA" |> p() 
 "Muslim"|> p()                                 
# "Native American"|> p()   
```

## Intersectional Group

```{r}
#| fig-width: 4
#| fig-height: 3


"Black men" |> p() 
"Black woman" |> p()  
"Black women" |> p()
```


# Outliers 

## DOT mentions of Citizenship 

DOT and FAA saw a massive spike in orders mentioning "Citizenship" related to a post 9/11 policy requiring owners of companies, including shipping companies and air taxis (small planes for hire?) to attest to whether they were owned by citizens that resulted in many businesses losing their aviation licenses and investigations into ownership of aviation businesses, including DHL and Virgin America. 

> Federal law requires U.S.-based air carriers to be U.S. "citizens." To qualify, the outstanding voting interests of the air carrier must be at least 75-percent owned by U.S. citizens and the carrier must also be effectively controlled by U.S. citizens.

https://news.alaskaair.com/newsroom/alaska-airlines-renews-request-for-open-dot-review-of-virgin-americas-ownership-status/

```{r eval=F}
rules_racial_all$searchTerm |> unique() 

rules_racial_all |> filter(agencyId == "DOT", 
                           searchTerm == "Citizenship") |> 
  distinct(id, documentType, highlightedContent) |> 
  arrange(-nchar(highlightedContent)) |> 
  kablebox()


```
